\documentclass{letter}
\usepackage{hyperref}

\signature{Steven Deobald}
\address{F3, Block 3 Shivani Apartments \\ Thiruvanmyuir, Chennai
\\ Tamil Nadu, India - 600041}

\begin{document}
\begin{letter}{ynharari \\ P.O. Box 3308 \\ Karmei Yosef 9979700
\\ Israel}

\opening{Dear Dr. Harari:}

I am interested in the meditation research you mention in Chapter 21 of
your latest book. On page 322 (of the printing I own) you mention:

\begin{quote}
``Some universities and laboratories have indeed begun using meditation as a research
tool rather than as a mere object for brain studies. Yet this process is still in its
infancy, partly because it requires an extraordinary investment on the part of the
researchers.''
\end{quote}

Unfortunately, this is one of the few references you make without including an
endnote. Or fortunately, perhaps, as it gives me an excuse to write you this
letter. I would love to know which universities and laboratories you refer to in this
passage precisely because my partner and I have a desire to make such an investment.

I am a computer scientist by trade and
an eye injury four years ago has restricted my computer use. My partner Preethi is
a geneticist who has tired of private industry and would like to return to
academia. We both left our jobs in July of 2018 to meditate more seriously and
consider the next step in our respective careers. (Re-)Entering academia seemed like
a natural fit for both of us and meditation topped our list of research topics but we
were entirely uncertain how to enter this field, and under what discipline.

Next month (March), Preethi will sit her fourth 10-Day Vipassana course and I will
sit my first 20-Day. You may write to our Chennai address at the top of this letter
or email us at steven@deobald.ca and preethi@deobald.ca.

\closing{Mangal bhav,}

\end{letter}
\end{document}
